COG-ED Manuscript

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
removed BF from pilot results H2a

`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis2a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing subjective values between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

>>>>

`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis2a_contrasts,
  caption = "Different contrasts for the rmANOVA comparing subjective values between n-back levels",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```
